---
title: "Module 3"
subtitle: "{{< var md-03.title >}}"
editor: source
params:
    module: 3
execute:
  echo: false
  warning: false
bibliography: references.bib
---

This module is a case study on data stewardship in practice, built around the Global Health Engineering (GHE) group at ETH Zurich. There is no lecture this week; you will read an interview, watch a talk, and reflect on whether and how the approach could apply to your own research context.

```{r}
#| label: setup

library(epoxy)
```

```{r}
#| label: learning-objectives

lobj <- readr::read_csv(here::here("data/tbl-02-learning-objectives.csv")) |>
  dplyr::filter(module == params$module) |>
  dplyr::pull(learning_objectives)

vars <- yaml::read_yaml(here::here("_variables.yml"))
session_date <- format(as.Date(vars$`md-03`$date), "%B %d, %Y")
homework_due_date <- format(as.Date(vars$`md-03`$`homework-due`), "%B %d, %Y")
```

## {{< fa bullseye >}} Learning Objectives

```{epoxy}
{1:length(lobj)}. {lobj[1:length(lobj)]}
```

## {{< fa book >}} Readings

{{< fa book >}} Read @wilson2017 "Good enough practices in scientific computing".

## {{< fa code >}} Homework assignment

[Due date:]{.highlight-yellow} `r homework_due_date`

Work through these assignments in order:

-   [Assignment 1 (am-03-1)](../assignments/md-03/am-03-1-bookmarks.qmd): Support yourself with bookmarks
-   [Assignment 2 (am-03-2)](../assignments/md-03/am-03-2-case-study.qmd): Case study, Data stewardship at ETH GHE
-   [Assignment 3 (am-03-3)](../assignments/md-03/am-03-3-github-clone.qmd): Clone a GitHub repository to Posit Cloud
-   [Assignment 4 (am-03-4)](../assignments/md-03/am-03-4-github-workflow.qmd): GitHub workflow, commit and push

Then complete the homework programming assignment that is in your project folder for Module 3 on [Posit Cloud]({{< var platforms.posit-cloud >}}content/all).

- hw-data-stewardship.qmd

## {{< fa pen-clip >}} Learning reflection

Complete the learning reflection that is in your project folder for Module 3 by [**`r homework_due_date`**]{.highlight-yellow} on [Posit Cloud]({{< var platforms.posit-cloud >}}content/all).

- learning-03.qmd
