---
title: "Module 1"
subtitle: "{{< var md-01.title >}}"
editor: source
params:
    module: 1
execute:
  echo: false
  warning: false
---

This first module gets you set up for the course. Work through the homework assignments one after the other.

```{r}
#| label: setup

library(epoxy)
```

```{r}
#| label: learning-objectives

lobj <- readr::read_csv(here::here("data/tbl-02-learning-objectives.csv")) |>
  dplyr::filter(module == params$module) |>
  dplyr::pull(learning_objectives)

vars <- yaml::read_yaml(here::here("_variables.yml"))
homework_due_date <- format(as.Date(vars$`md-01`$`homework-due`), "%B %d, %Y")
```

## {{< fa bullseye >}} Learning Objectives

```{epoxy}
{1:length(lobj)}. {lobj[1:length(lobj)]}
```

## {{< fa book >}} Readings

{{< fa book >}} Read the [Course Overview](../index.html) and pay special attention to the sections Assignments, Grading scheme, and late work.

## {{< fa code >}} Homework assignments

[Due date:]{.highlight-yellow} `r homework_due_date`

These homework assignments are pre-requisites for Module 2. Please complete them before the due date.

-   [Assignment 1](../assignments/md-01/am-01-1-github-account.qmd): Get an account for GitHub
-   [Assignment 2](../assignments/md-01/am-01-2-orcid.qmd): Create your personal unique ORCID iD
-   [Assignment 3](../assignments/md-01/am-01-3-posit-cloud.qmd): Log into Posit Cloud and join the course workspace
-   [Assignment 4](../assignments/md-01/am-01-4-github-pat.qmd): Set up a GitHub Personal Access Token
-   [Assignment 5](../assignments/md-01/am-01-5-pre-course-survey.qmd): Complete the pre-course survey
-   [Assignment 6](../assignments/md-01/am-01-6-github-issue.qmd): Prepare questions and open an issue on GitHub

## Thanks! {{< fa sun >}}

Thank you for working through these assignments. I am looking forward to meeting you in Module 2.
