---
title: "Module 4"
subtitle: "{{< var md-04.title >}}"
editor: source
params:
    module: 4
execute:
  echo: false
  warning: false
---

```{r}
#| label: setup

library(epoxy)
```

```{r}
#| label: learning-objectives

lobj <- readr::read_csv(here::here("data/tbl-02-learning-objectives.csv")) |>
  dplyr::filter(module == params$module) |>
  dplyr::pull(learning_objectives)

vars <- yaml::read_yaml(here::here("_variables.yml"))
session_date <- format(as.Date(vars$`md-04`$date), "%B %d, %Y")
homework_due_date <- format(as.Date(vars$`md-04`$`homework-due`), "%B %d, %Y")
```

## {{< fa bullseye >}} Learning Objectives

```{epoxy}
{1:length(lobj)}. {lobj[1:length(lobj)]}
```

## {{< fa display >}} Slides

[View slides in full screen](../slides/lec-02-visualisation.html) | [Download slides as PDF]({{< var course.github-org >}}/website/raw/main/slides/lec-02-visualisation.pdf)

```{=html}
<iframe class="slide-deck" src="../slides/lec-02-visualisation.html" height="420" width="747" style="border: 1px solid #123233;"></iframe>
```

## {{< fa book >}} Readings

1. Read [R for Data Science - Section 3 to 3.6 - Data visualisation](https://r4ds.had.co.nz/data-visualisation.html)
2. Read [Fundamentals of Data Visualization - Section 2 - Visualizing data: Mapping data onto aesthetics](https://clauswilke.com/dataviz/aesthetic-mapping.html)
3. Read [Data Organization in Spreadsheets](https://www.tandfonline.com/doi/full/10.1080/00031305.2017.1375989)

## {{< fa code >}} Homework assignment

[Due date:]{.highlight-yellow} `r homework_due_date`

Complete the homework programming assignment that is in your project folder for Module 4 on [Posit Cloud]({{< var platforms.posit-cloud >}}content/all).

- hw-data-visualisation.qmd
- hw-project-data.qmd

## {{< fa pen-clip >}} Learning reflection

Complete the learning reflection that is in your project folder for Module 4 by [**`r homework_due_date`**]{.highlight-yellow} on [Posit Cloud]({{< var platforms.posit-cloud >}}content/all).

- learning-04.qmd

## {{< fa video >}} Session Recording

You can access the recording of the Module 4 session held on `r session_date`.

[Recording link will be added after the live session.]{.highlight-yellow}
