---
title: "Module 6"
subtitle: "{{< var md-06.title >}}"
editor: source
params:
    module: 6
execute:
  echo: false
  warning: false
---

```{r}
#| label: setup

library(epoxy)
```

```{r}
#| label: learning-objectives

lobj <- readr::read_csv(here::here("data/tbl-02-learning-objectives.csv")) |>
  dplyr::filter(module == params$module) |>
  dplyr::pull(learning_objectives)

vars <- yaml::read_yaml(here::here("_variables.yml"))
session_date <- format(as.Date(vars$`md-06`$date), "%B %d, %Y")
homework_due_date <- format(as.Date(vars$`md-06`$`homework-due`), "%B %d, %Y")
```

## {{< fa bullseye >}} Learning Objectives

```{epoxy}
{1:length(lobj)}. {lobj[1:length(lobj)]}
```

## {{< fa display >}} Slides

[View slides in full screen](../slides/lec-04-tidy-data.html) | [Download slides as PDF]({{< var course.github-org >}}/website/raw/main/slides/lec-04-tidy-data.pdf)

```{=html}
<iframe class="slide-deck" src="../slides/lec-04-tidy-data.html" height="420" width="747" style="border: 1px solid #123233;"></iframe>
```

## {{< fa book >}} Readings

1. Read [R for Data Science - Section 12 - Tidy data](https://r4ds.had.co.nz/tidy-data.html)
2. Read [R for Data Science - Section 15 - Factors](https://r4ds.had.co.nz/factors.html#factors)

## {{< fa code >}} Homework assignment

[Due date:]{.highlight-yellow} `r homework_due_date`

Complete the homework programming assignments that are in your project folder for Module 6 on [Posit Cloud]({{< var platforms.posit-cloud >}}content/all):

- hw-tidyr.qmd

Complete the following assignment, which is not documented in your Module 6 project folder:

- [HW: Capstone Project Data Exploration](../assignments/hw-05-project-data-exploration.qmd)

## {{< fa pen-clip >}} Learning reflection

Complete the learning reflection that is in your project folder for Module 6 by [**`r homework_due_date`**]{.highlight-yellow} on [Posit Cloud]({{< var platforms.posit-cloud >}}content/all).

- learning-06.qmd

## {{< fa video >}} Session Recording

You can access the recording of the Module 6 session held on `r session_date`.

[Recording link will be added after the live session.]{.highlight-yellow}
