---
title: "Capstone Project"
editor: source
params:
    module: 8
execute: 
  echo: false
  warning: false
editor_options: 
  chunk_output_type: console
---


```{r}
library(tidyverse)

grading <- read_csv(here::here("data/tbl-04-capstone-project-grading.csv")) 
```


The Capstone Project report is the last assignment of the course and contributes 40% to the total grade (see [Course Overview](../index.qmd)). The final two weeks are reserved for working on the report. 


## {{< fa bullseye >}} Learning Objectives

```{r}

lobj1 <- readr::read_csv(here::here("data/tbl-02-learning-objectives.csv")) |> 
  dplyr::filter(week == params$week) |>
  dplyr::pull(learning_objectives)

```

1. `r lobj1[1]`


## {{< fa code >}} GitHub repository

A repository for each student is established during week 4 of the course (see [HW 04b: Capstone Project Setup](../assignments/hw-04b-capstone-project-setup.qmd)). Students begin exploring their data and performing initial tidying in week 5 (see [HW 05: Project Data Exploration](../assignments/hw-05-project-data-exploration.qmd)). This repository contains self-identified data that was shared in week 3 of the course. Some data cleaning steps may be performed by the course instructor, so that each student has a tidy dataset to work with.

The repository further contains an empty Quarto file (index.qmd), which students must use to write their report. A list of graded items was prepared to guide students in writing the report.

## {{< fa pen-clip >}} GitHub issue tracker

The GitHub issue tracker of each student's capstone project repository is used to communicate and ask questions about the Capstone Project report.

## {{< fa calendar-check >}} Submission due date

The due date for submission of the report is [**{{< var md-08.homework-due >}}**]{.highlight-yellow}. Any commits after the due date will not be counted against the graded items. 

## {{< fa list-check >}} Graded items

@tbl-grading-items is a detailed list of items for grading of the capstone project report are presented. The sum of points is 100 and spread over technical and intellectual items as presented in @tbl-grading-categories.

```{r}
#| label: tbl-grading-items
#| tbl-cap: "List of items and points for grading of the capstone project report."

grading %>% 
  select(category, items, points) %>% 
  knitr::kable()

```

```{r}
#| label: tbl-grading-categories
#| tbl-cap: "Sum of points for technical and intellectual part of report."

grading |> 
  group_by(category, description) |> 
  summarise(points = sum(points)) |> 
  knitr::kable()

```

