---
title: "Capstone Project"
editor: source
params:
    week: 7
execute: 
  echo: false
  warning: false
editor_options: 
  chunk_output_type: console
---


```{r}
library(tidyverse)

grading <- read_csv(here::here("data/tbl-04-capstone-project-grading.csv")) 
```


The Capstone Project report is the last assignment of the course and contributes 40% to the total grade (see [Course Overview](../index.qmd)). The final two weeks are reserved for working on the report. 


## {{< fa bullseye >}} Learning Objectives

```{r}

lobj1 <- readr::read_csv(here::here("data/tbl-02-learning-objectives.csv")) |> 
  dplyr::filter(week == params$week) |>
  dplyr::pull(learning_objectives)

```

1. `r lobj1[1]`


## {{< fa code >}} GitHub repository

A repository for each student is established during week 4 of the course (see [HW 04b: Capstone Project Setup](../assignments/hw-04b-capstone-project-setup.qmd)). This repository contains self-identified data that was shared in week 3 of the course. Some data cleaning steps are performed by the course instructor, so that each student has a tidy dataset to work with.

The repository further contains an empty Quarto file (report.qmd), which students must use to write their report. A list of graded items was prepared to guide students in writing the report.

## {{< fa pen-clip >}} GitHub issue tracker

The GitHub issue tracker of each student's capstone project repository is used to communicate and ask questions about the Capstone Project report.

## {{< fa calendar-check >}} Submission due date

The due date for submission of the report is [**{{< var md-08.homework-due >}}**]{.highlight-yellow}. Any commits after the due date will not be counted against the graded items. 

## {{< fa list-check >}} Graded items

@tbl-grading-items is a detailed list of items for grading of the capstone project report are presented. The sum of points is 100 and spread over technical and intellectual items as presented in @tbl-grading-categories.

```{r}
#| label: tbl-grading-items
#| tbl-cap: "List of items and points for grading of the capstone project report."

grading %>% 
  select(category, items, points) %>% 
  knitr::kable()

```

```{r}
#| label: tbl-grading-categories
#| tbl-cap: "Sum of points for technical and intellectual part of report."

grading |> 
  group_by(category, description) |> 
  summarise(points = sum(points)) |> 
  knitr::kable()

```

## {{< fa folder >}} Directory structure

Once your capstone project repository is set up (completed in [HW 04b](../assignments/hw-04b-capstone-project-setup.qmd)), organize your project with the following directory structure:

### Required folders

- `data/` - Store your datasets and related files
- `docs/` - Documentation and supplementary materials

### Data folder organization

Your `data/` folder should be well-documented to ensure reproducibility. Create a `README.md` file in the `data/` folder that includes:

- **Data source information**: Where the data comes from
- **Data collection methods**: How the data was collected
- **Variable descriptions**: What each column/variable represents
- **Data processing notes**: Any cleaning or transformation steps
- **File descriptions**: What each data file contains
- **Date information**: When the data was collected/last updated

Use the template from: https://raw.githubusercontent.com/rbtl-dev/metadata-readme-template/main/README.md

## {{< fa terminal >}} Getting started

1. Access your capstone project repository on [Posit Cloud]({{< var platforms.posit-cloud >}}content/all?sort=name_asc)
2. Ensure you have completed the directory structure setup from [HW 04b](../assignments/hw-04b-capstone-project-setup.qmd)
3. Begin working on your `report.qmd` file using the graded items below as guidance

